% 设定文章类型与编码格式
\documentclass[UTF8]{report}		
\input{D:/a_RemoteRepo/GH.LatexNotes/.config/ConfigForBooks.tex}  % 引用导言区设置



% ------------------------ 文章信息区 ------------------------ %
% ------------------------ 文章信息区 ------------------------ %

\lhead{\small
\href{https://github.com/YiDingg/LatexNotes}{\color{black}\faGithub\ https://github.com/YiDingg/LatexNotes}
}
\chead{Analog Components Handbook}
\rhead{\small dingyi233@mails.ucas.ac.cn}

%文档信息设置
\title{模拟电路元件手册\\ Analog Components Handbook}
\author{丁毅\\ \footnotesize {\kaishu (中国科学院大学，北京 100049)} \\ Yi Ding \\ \footnotesize \textit{(University of Chinese Academy of Sciences, Beijing 100049, China)}}
\date{\footnotesize 2024.11 -- ...}

% ------------------------ 文章信息区 ------------------------ %
% ------------------------ 文章信息区 ------------------------ %


% 开始编辑文章
\begin{document} 
\zihao{5}           % 设置全文字号大小

% ------------------------ 封面序言与目录 ------------------------ %
% >> --------------------- 封面序言与目录 --------------------- << %
% 封面
    \maketitle\newpage  
    \pagenumbering{Roman} % 页码为大写罗马数字
    \thispagestyle{fancy}   % 显示页码、页眉等

% 序言
\begin{cnabstract}\normalsize 
本书为笔者本科时的“模拟电路元件手册”，对学习过程中接触较多的模拟元件作了简要的介绍和总结，同时也是具体元件的测试记录本。笔者所使用过的大多数元件，都进行了较为详细的实际测试，结果记录在本手册中。本书不仅能帮助读者快速了解各类模拟元件的基本信息，还能为读者的元件选型提供参考数据，进而提高电路的设计效率。

本手册将长期更新，读者可到我的 GitHub 下载手册的最新版本 \href{https://github.com/YiDingg/LatexNotes}{https://github.com/YiDingg/LatexNotes}，也可以在我的个人网站 \href{URL}{待更新} 上找到相关资料。

事实上，有相当一部分元件（例如 Operational Amplifier ）是基础元件所构成的模块化电路。在本书，我们不会详谈如何搭建出这些模块电路，而是讨论如何对这些模块建立正确的认识，介绍在不同情况下应该选用怎样的模型进行分析，以达到足够高的精度，同时尽可能地降低模型复杂度。实现它们的具体电路，以及 Oscillators, Amplifiers 等模块元件及其应用电路，会放到另一本书{\kaishu 《模拟电路手册》}中，读者可到网址 \href{https://github.com/YiDingg/LatexNotes/tree/main/%5BNotes%5D%20Electornic%20Circuits%20Manual}{GitHub {\color{black} (https://github.com/YiDingg/LatexNotes/tree/main/[Notes] Electornic Circuits Manual)}} 自行下载和阅读。


为了提高读者的自学效率，笔者在这里推荐几个免费而优秀的电子学习网站：
\begin{enumerate}
\item \href{https://www.electronics-tutorials.ws/}{Electornics Tutorials} : 这个网站提供了丰富的电子学习资料，包括 Transistors, Amplifiers, Diodes, Filters 等，还提供了很多实用的电子工程师工具，例如在线电阻电感电容计算器等；

\item \href{https://www.learnabout-electronics.org/}{Learn About Electronics} : 这个网站提供了电子学习的基础和进阶知识，包括 Semiconductors, Amplifiers, Oscillators, Power Supplies 等，最令人惊喜的是几乎所有资料都提供了 PDF 下载，方便读者下载后自行学习；

\item \href{https://www.electronics-lab.com}{Electronics Lab} : 这个网站不仅开源了很多电子电路设计实例，包括基础电路、模拟电路、数字电路等，还提供了丰富的学习资源（文章）在 \href{https://www.electronics-lab.com/articles/}{here}；

\item \href{https://developerhelp.microchip.com/}{Microchip} : 这是 Microchip 官方的开发者帮助网站，提供了大量的电子元件的 Data Sheet, Application Notes, Reference Manuals 等，是学习 Microchip 产品的重要参考网站，当然，在这里也可以找到与模拟电路、数字电路相关的的学习资料；

\item \href{https://wiki.analog.com/university/courses/tutorials/index}{Analog Devices {\color{black}(https://wiki.analog.com/university/courses/tutorials/index)}} : 这是 Analog Devices 官方的 Wiki 网站，提供了大量的电子学习资料，包括 Analog Electronics, Mixed Signal Electronics (Systems), Signals and Systems 以及 some e-books in PDF ，是学习模拟电路的优秀网站。

\item \item \href{https://www.allaboutcircuits.com/technical-articles/}{  All About Circuits  {\color{black} (https://www.allaboutcircuits.com/technical-articles/)}} : 这个网站提供了丰富的电子电路和教程，同时收集了大量的模拟电路设计参考。
\end{enumerate}

由于个人学识浅陋，认识有限，文中难免有不妥甚至错误之处，望读者不吝指正，也欢迎内容、排版等方面的建议。读者可以将错误或建议发送到我的邮箱 {\color{blue}\ dingyi233@mails.ucas.ac.cn}，也可以到笔者的 \href{https://github.com/YiDingg/LatexNotes}{GitHub (https://github.com/YiDingg/LatexNotes)} 上提 issue ，衷心感谢。

\end{cnabstract}
\addcontentsline{toc}{chapter}{序言} % 手动添加为目录



\newpage
\begin{enabstract}
    \zihao{5}
    This is an analog components handbook during my undergraduate studies. It provides a summary of the components that I encountered frequently during my studies, and is also a test record book for specific components. Most of the components I have used have been tested in detail, and the results are recorded in this handbook. This book can not only help readers quickly understand the basic information of various analog components, but also provide reference data for readers' components selection, thereby improving the efficiency of circuit design.

    This handbook will be updated for a long time. Readers can download the latest version of the handbook from my GitHub \href{https://github.com/YiDingg/LatexNotes}{https://github.com/YiDingg/LatexNotes}, and can also find related materials on my personal website \href{URL}{to be updated}.

    

    Additionally, there are a variety number of components (such as Operational Amplifier) that are actually modular circuits comprised of basic components. In this book, we will not delve into how to build these advanced components, but rather discuss how to properly understand these components (modular circuits), and explore the models that should be used for analysis in different situations to achieve sufficient accuracy, while minimizing model complexity. The specific circuits for constructing these components, such as oscillators, amplifiers, etc., will be included in another book \textit{``Analog Circuits Handbook''}, which can also be found on my \href{https://github.com/YiDingg/LatexNotes/tree/main/%5BNotes%5D%20Electornic%20Circuits%20Manual}{GitHub > YiDingg > Analog Circuits Handbook}. 
    
    In order to better enhance the reader's self-study efficiency, I recommend several free and excellent online learning websites here: 
    \begin{enumerate}
    \item \href{https://www.electronics-tutorials.ws}{Electronics Tutorials {\color{black} (https://www.electronics-tutorials.ws)}}: This website provides a wealth of electronic learning resources, including Transistors, Amplifiers, Diodes, Filters, and many practical tools for electronic engineers, such as an online resistor, inductor, and capacitor calculator.
    
    \item \href{https://www.learnabout-electronics.org}{  Learn About Electronics  {\color{black} (https://www.learnabout-electronics.org)}}: The website provides basic and advanced knowledge of electronics, including Semiconductors, Amplifiers, Oscillators, Power Supplies, and the best part is that almost all the materials are provided in PDF format for easy download and offline learning.
    
    \item \href{https://www.electronics-lab.com}{  Electronics Lab  {\color{black} (https://www.electronics-lab.com)}}: This website not only open-source many electronic circuit design examples, including basic circuits, analog circuits, and digital circuits, but also provides a wealth of learning resources and articles \href{https://www.electronics-lab.com/articles/}{here {\color{black} (https://www.electronics-lab.com/articles)}}.

    \item \href{https://developerhelp.microchip.com}{  Microchip  {\color{black} (https://developerhelp.microchip.com)}}: This is Microchip's official developer help website which provides a wealth of data sheets, application notes, and reference manuals for electronic components. It is an important reference website for learning about Microchip products, and of course, you can also find learning materials related to analog circuits and digital circuits here. 
    
    \item \href{https://wiki.analog.com/university/courses/tutorials/index}{Analog Devices {\color{black}(https://wiki.analog.com/university/courses/tutorials/index)}} : This is Analog Devices' official Wiki website, which provides a wealth of electronic learning materials, including Analog Electronics, Mixed Signal Electronics (Systems), Signals and Systems, and some eBooks in PDF, which is an excellent website for learning analog circuits.

    \item \href{https://www.allaboutcircuits.com/technical-articles/}{  All About Circuits  {\color{black} (https://www.allaboutcircuits.com/technical-articles/)}}: This website provides a wealth of electronic circuits and tutorials, and collects numerous analog circuits.
\end{enumerate}
    
    Due to my own limited knowledge and understanding, there may be inappropriate or even incorrect parts in this article. I sincerely hope readers will point out any errors or inaccuracies. Readers can send errors to my email address {\color{blue} dingyi233@mails.ucas.ac.cn}, or report issues on my \href{https://github.com/YiDingg/LatexNotes}{GitHub {\color{black} (https://github.com/YiDingg/LatexNotes)}} with my utmost gratitude.
\end{enabstract}
\addcontentsline{toc}{chapter}{Preface} % 手动添加为目录



% 目录
    \setcounter{tocdepth}{2}    % 目录深度 (为 1 时显示到 section)
    % 目录页
        \tableofcontents
        \addcontentsline{toc}{chapter}{Contents}
        \thispagestyle{fancy}                   % 显示页码、页眉等
    % 插图页
        %\cleardoublepage\listoffigures
        %\addcontentsline{toc}{chapter}{插图}
        %\thispagestyle{fancy}                   % 显示页码、页眉等
    % 表格页
        %\cleardoublepage\listoftables
        %\addcontentsline{toc}{chapter}{表格}
        %\thispagestyle{fancy}                   % 显示页码、页眉等 

% 收尾工作
    \newpage    
    \pagenumbering{arabic} 


% >> --------------------- 封面序言与目录 --------------------- << %
% ------------------------ 封面序言与目录 ------------------------ %



\subfile{contents/Chapter on Diodes/Analog_Components_Handbook (Diodes).tex}
\subfile{contents/Chapter on Transistors/Analog_Components_Handbook (Transistors).tex}
\subfile{contents/Chapter on Inductors/Analog_Components_Handbook (Inductors).tex}
\subfile{contents/Chapter on Capacitors/Analog_Components_Handbook (Capacitors).tex}

%\chapter{Amplifiers}\thispagestyle{fancy}
%\section{Common Emitter Amplifier (共射极放大器)}
%\section{Common Base Amplifier (共基放大器)}
%\section{Common Collector Amplifier (共集放大器)}
%\section{Common Source Amplifier (共源放大器)}
%\section{MOSFET Amplifier (MOSFET 放大器)}
%\subsection{LM258P}
%\subsection{NE5532P}
%\subsection{LM318N}
%\section{Class AB Amplifier (AB 类放大器)}


\renewcommand{\bibname}{Reference}  % 将参考文献标题从 bibliography 改为 Reference
\nocite{*}
\bibliography{bibtex}
\thispagestyle{fancy} 
\addcontentsline{toc}{chapter}{Reference}


\end{document}



% VScode 常用快捷键：

% F2:                       变量重命名
% Ctrl + Enter:             行中换行
% Alt + up/down:            上下移行
% 鼠标中键 + 移动:           快速多光标
% Shift + Alt + up/down:    上下复制
% Ctrl + left/right:        左右跳单词
% Ctrl + Backspace/Delete:  左右删单词    
% Shift + Delete:           删除此行
% Ctrl + J:                 打开 VScode 下栏(输出栏)
% Ctrl + B:                 打开 VScode 左栏(目录栏)
% Ctrl + `:                 打开 VScode 终端栏
% Ctrl + 0:                 定位文件
% Ctrl + Tab:               切换已打开的文件(切标签)
% Ctrl + Shift + P:         打开全局命令(设置)

% Latex 常用快捷键

% Ctrl + Alt + J:           由代码定位到PDF
% 


% Git提交规范：
% update: Linear Algebra 2 notes
% add: Linear Algebra 2 notes
% import: Linear Algebra 2 notes
% delete: Linear Algebra 2 notes